Untitled

### 2015-02-04 documentation/analytical.Rmd
work on analytical solution, simplifications

<!--

m*K*x-(2-a*m*h-a*L)*K*y*x + (m-2*a*m*h-2*a*L)*K*y^2*x+ a*m*h*K*y^3*x + a*L*K*y^3*x+ (v*L-a*L*p)*K*y^-1*x^2 + (v*m*h-a*L*p+v*L)*K*y*x^2- 2*v*m*h*K*y^2*x^2 + v*m*h*K*y^3*x^2+ 2*a*L*p*K*x^2 - 2*v*L*K*x^2 - v*L*p*K*y^(-2)*x^3 + 2*v*L*p*K*y^(-1)*x^3 - v*L*p*K*x^3    - b*r*K*y^2  + (b*r+f*r-b*r*f+b*a*r*h)*K*y^3  + (b*a*r*h+f*a*r*h-b*f*a*r*h)*K y^4  + b*r*K*y*x + (2*f*r+b*r-b*r*a*h+ b*v*r*h)*K*y^2*x + (2*f*a*r*h + b*r*a*h-b*v*r*h-f*v*r*h+b*f*v*r*h)*K*y^3*x - (f*r +b*r*f- b*v*r*h)*K*y*x^2 - (r*a*h*f +b*f*r*a*h+ b*v*r*h)*K*y^2*x^2 - (f*v*r*h +b*v*r*h*f)*K*y*x^3     + b*r*y^3  - (b*r+f*r-b*r*f+ b*a*r*h)*y^4  - (b*a*r*h+f*a*r*h-b*f*a*r*h)*y^5  - b*r*y^2*x- (2*f*r+b*r-b*r*a*h+ b*v*r*h)*y^3*x - (2*f*a*r*h + b*r*a*h-b*v*r*h-f*v*r*h+b*f*v*r*h)*y^4*x+ (f*r +b*r*f- b*v*r*h)*y^2*x^2 + (r*a*h*f +b*f*r*a*h+ b*v*r*h)*y^3*x^2 + (f*v*r*h +b*v*r*h*f)*y^2*x^3     - m*K*y*x + (2-a*m*h-a*L)*K*y^2*x - (m- 2*a*m*h- 2*a*L)*K *y^3*x- a*m*h*K*y^4*x - a*L*K*y^4*x- (v*L- a*L*p)*K*x^2 - (v*m*h- a*L*p+ v*L)*K*y^2*x^2+ 2*v*m*h*K*y^3*x^2 - v*m*h*K*y^4*x^2- 2*a*L*p*K*y*x^2 + 2*v*L*K*y*x^2 + v*L*p*K*y^(-1)*x^3 - 2*v*L*p*K*x^3 + v*L*p*K*y*x^3   + b*r*K*y^3  - (b*r+f*r-b*r*f+ b*a*r*h)*K*y^4  - (b*a*r*h+f*a*r*h-b*f*a*r*h)*K*y^5  - b*r*K*y^2*x- (2*f*r+b*r-b*r*a*h+ b*v*r*h)*K*y^3*x - (2*f*a*r*h + b*r*a*h-b*v*r*h-f*v*r*h+b*f*v*r*h)*K*y^4*x+ (f*r +b*r*f- b*v*r*h)*K*y^2*x^2  + (r*a*h*f +b*f*r*a*h+ b*v*r*h)*K*y^3*x^2 + (f*v*r*h +b*v*r*h*f)*K*y^2*x^3     - b*r*y^4  + (b*r+f*r-b*r*f+ b*a*r*h)*y^5  + (b*a*r*h+f*a*r*h-b*f*a*r*h)*y^6  + b*r*y^3*x+ (2*f*r+b*r-b*r*a*h+ b*v*r*h)*y^4*x + (2*f*a*r*h+b*r*a*h-b*v*r*h-f*v*r*h+b*f*v*r*h)*y^5*x- (f*r +b*r*f- b*v*r*h)*y^3*x^2  - (r*a*h*f+b*f*r*a*h+b*v*r*h)*y^4*x^2 - (f*v*r*h +b*v*r*h*f)*y^3*x^3     + b*r*K*c*y^3  - (b*r+f*r-b*r*f+ b*a*r*h)*K*c*y^4  - (b*a*r*h+f*a*r*h-b*f*a*r*h)*K*c*y^5  - b*r*K*c* y^2*x- (2*f*r+b*r-b*r*a*h+ b*v*r*h)*K*c*y^3*x - (2*f*a*r*h + b*r*a*h-b*v*r*h-f*v*r*h+b*f*v*r*h)*K*c*y^4*x+ (f*r +b*r*f- b*v*r*h)*K*c*y^2*x^2  + (r*a*h*f +b*f*r*a*h+ b*v*r*h)*K*c*y^3*x^2 + (f*v*r*h+b*v*r*h*f)*K*c*y^2*x^3     - m*K*c*y*x + (2-a*m*h-a*L)*K*c*y^2*x - (m- 2*a*m*h- 2*a*L)*K*c*y^3*x - a*m*h*K*c*y^4*x - a*L*K*c*y^4*x- (v*L- a*L*p)*K*c*x^2 - (v*m*h-a*L*p+v*L)*K*c*y^2*x^2+ 2*v*m*h*K*c* y^3*x^2 - v*m*h*K*c*y^4*x^2- 2*a*L*p*K*c*y*x^2 + 2*v*L*K*c*y*x^2 + v*L*p*K*c*y^(-1)*x^3 - 2*v*L*p*K*c*x^3 + v*L*p*K*c*y*x^3    + m*K*c*x^2 - (2-a*m*h-a*L)*K*c*y*x^2 + (m- 2*a*m*h-2*a*L)*K*c*y^2*x^2+ a*m*h*K*c*y^3*x^2 + a*L*K*c*y^3*x^2+ (v*L- a*L*p)*K*c*y^(-1)*x^3 + (v*m*h-a*L*p+v*L)*K*c*y*x^3 - 2*v*m*h*K*c*y^2*x^3 + v*m*h*K*c*y^3*x^3 + 2*a*L*p*K*c*x^3 - 2*v*L*K*c*x^3 - v*L*p*K*c*y^(-2)*x^4 + 2*v*L*p*K*c*y^(-1)*x^4 - v*L*p*K*c*x^4    - b*r*K*c*y^2*x + (b*r+f*r-b*r*f+b*a*r*h)*K*c*y^3*x + (b*a*r*h+f*a*r*h-b*f*a*r*h)*K*c*y^4*x + b*r*K*c*y*x^2 + (2*f*r+b*r-b*r*a*h+ b*v*r*h)*K*c*y^2*x^2 + (2*f*a*r*h+b*r*a*h-b*v*r*h-f*v*r*h+b*f*v*r*h)*K*c*y^3*x^2 - (f*r+b*r*f-b*v*r*h)*K*c*y*x^3 - (r*a*h*f+b*f+r*a*h+b*v*r*h)*K*c*y^2*x^3 - (f*v*r*h+b*v*r*h*f)*K*c*y*x^4 = 0

-->

>>>>

$$0 =  (br+fr-brf+ barh)K \rho_1^{3} - brK \rho_1^{2} + (barh+farh-bfarh)K \rho_1^{4}   + br \rho_1^{3} - (br+fr-brf+ barh) \rho_1^{4} - (barh+farh-bfarh) \rho_1^{5} + brK \rho_1^{3}   - (br+fr-brf+ barh)K \rho_1^{4}- (barh+farh-bfarh)K \rho_1^{5}  - br \rho_1^{4} + (br+fr-brf+ barh) \rho_1^{5} + (barh+farh-bfarh) \rho_1^{6}  + brKc \rho_1^{3} - (br+fr-brf+ barh)Kc \rho_1^{4} - (barh+farh-bfarh)Kc \rho_1^{5}+ ( mK + (m- 2amh- 2aL)K \rho_1^{2} - (2-amh-aL)K \rho_1 + amhK \rho_1^{3} + aLK \rho_1^{3} + brK \rho_1 + (2fr+br-brah+ bvrh)K \rho_1^{2} + (2farh + brah-bvrh-fvrh+bfvrh)K\rho_1^{3} - br \rho_1^2- (2fr+br-brah+ bvrh) \rho_1^{3}  - (2farh + brah-bvrh-fvrh+bfvrh)\rho_1^{4} - mK \rho_1 + (2-amh-aL)K \rho_1^2  - (m- 2amh- 2aL)K \rho_1^{3}- amhK \rho_1^{4} - aLK \rho_1^{4}- brK \rho_1^2- (2fr+br-brah+ bvrh)K \rho_1^{3} - (2farh + brah-bvrh-fvrh+bfvrh)K\rho_1^{4}+ br \rho_1^3+ (2fr+br-brah+ bvrh) \rho_1^{4} + (2farh + brah-bvrh-fvrh+bfvrh)\rho_1^{5} - brKc \rho_1^2- (2fr+br-brah+ bvrh)Kc \rho_1^{3} - (2farh + brah-bvrh-fvrh+bfvrh)Kc\rho_1^{4} - mKc \rho_1 + (2-amh-aL)Kc \rho_1^2 - (m- 2amh- 2aL)Kc \rho_1^{3}- amhKc \rho_1^{4} - aLKc \rho_1^{4} - brKc \rho_1^{2} + (br+fr-brf+ barh)Kc \rho_1^{3} + (barh+farh-bfarh)Kc \rho_1^{4} ) \rho_{11}+ ((vL- aLp)K  \rho_1^{-1} + (vmh- aLp+ vL)K \rho_1- 2vmhK \rho_1^2 + vmhK \rho_1^{3}+ 2aLpK  - 2vLK   - (fr +brf- bvrh)K \rho_1 - (rahf +bfrah+ bvrh)K\rho_1^{2} + (fr +brf- bvrh) \rho_1^2  + (rahf +bfrah+ bvrh)\rho_1^{3}- (vL- aLp)K  - (vmh- aLp+ vL)K \rho_1^2 + 2vmhK \rho_1^3  - vmhK \rho_1^{4}- 2aLpK \rho_1  + 2vLK \rho_1   + (fr +brf- bvrh)K \rho_1^2  + (rahf +bfrah+ bvrh)K\rho_1^{3}   - (fr +brf- bvrh) \rho_1^3  - (rahf +bfrah+ bvrh)\rho_1^{4}  + (fr +brf- bvrh)Kc \rho_1^2  + (rahf +bfrah+ bvrh)Kc\rho_1^{3} - (vL- aLp)Kc  - (vmh- aLp+ vL)Kc \rho_1^2+ 2vmhKc \rho_1^3 - vmhKc \rho_1^{4}- 2aLpKc \rho_1  + 2vLKc \rho_1 + mKc  - (2-amh-aL)Kc \rho_1 + (m- 2amh- 2aL)Kc \rho_1^{2}+ amhKc \rho_1^{3} + aLKc \rho_1^{3}+ brKc \rho_1 + (2fr+br-brah+ bvrh)Kc \rho_1^{2} + (2farh + brah-bvrh-fvrh+bfvrh)Kc\rho_1^{3})\rho_{11}^2- (vLpK \rho_1^{-2} + 2vLpK \rho_1^{-1} - vLpK   - (fvrh +bvrhf)K\rho_1+ (fvrh +bvrhf)\rho_1^2  + vLpK \rho_1^{-1}    - 2vLpK  + vLpK \rho_1 + (fvrh +bvrhf)K\rho_1^2  - (fvrh +bvrhf)\rho_1^3+ (fvrh +bvrhf)Kc\rho_1^2 + vLpKc \rho_1^{-1} - 2vLpKc  + vLpKc \rho_1  + (vL- aLp)Kc  \rho_1^{-1} + (vmh- aLp+ vL)Kc \rho_1- 2vmhKc \rho_1^2 + vmhKc \rho_1^{3}+ 2aLpKc  - 2vLKc  - (fr +brf- bvrh)Kc \rho_1 - (rahf +bfrah+ bvrh)Kc\rho_1^{2} ) \rho_{11}^3- (vLpKc \rho_1^{-2} + 2vLpKc \rho_1^{-1} - vLpKc  - (fvrh +bvrhf)Kc\rho_1 ) \rho_{11}^4$$

$$0 = - brK \rho_1^{2}  + (br+2brK+rfK-brfK+barhK+brKc) \rho_1^{3}- (brKc-2br+frKc-brfKc+barhKc-brK-frK+brfK+farhK-bfarhK-fr+brf-barh) \rho_1^{4} + (br+fr-brf-barhK-farhK+bfarhK-farh+bfarh-barhKc-farhKc+bfarhKc) \rho_1^{5}+ (barh+farh-bfarh) \rho_1^{6}        + (mK + (brK-mK-mKc-2K+amhK+aLK) \rho_1 + (mK- br- 2amKh- 2aLK+2frK+brK-brahK+ bvrhK+2K-amhK-aLK- brK- 2brKc+ 2Kc-amhKc-aLKc) \rho_1^{2}   + (-mK-mKc+aLK-br++3amhK2farhK+2brahK-2bvrhK-fvrhK+bfvrhK-2fr+brah-bvrh-2frK+2aLK-2frKc+brahKc-bvrhKc+2amhKc+2aLKc+frKc-brfKc+barhKc) \rho_1^{3}-  (2farh-fvrh+bfvrh-amhK-aLK-2farhK-brahK+bvrhK+fvrhK-bfvrhK+2fr+br-amhKc-aLKc-bfarhKc-farhKc +bvrhKc+fvrhKc-bfvrhKc )\rho_1^{4} + (2farh + brah-bvrh-fvrh+bfvrh)\rho_1^{5}  )     \rho_{11}

+ ((vLK- aLpK)\rho_1^{-1}+ 2aLpK  - 2vLK - vLK+ aLpK - vLKc+ aLpKc + mKc+ (vmhK+vLK-frK-brfK+bvrhK-3aLpK+2vLK-2aLpKc+2vLKc-2Kc+amhKc+aLKc+brKc) \rho_1  + (2frKc+frbrf-bvrh+brKc-brahKc+ bvrhKc- 2vmhK+frK+brfK-bvrhK- rahfK -bfrahK-bvrhK- vmhK+ aLpK- vLK + frKc+brfKc- bvrhKc +mKc- 2amhKc- 2aLKc-vmhKc+aLpKc- vLKc) \rho_1^{2} + (3farhKc + brahKc-fvrhKc+bfvrhKc+ vmhK+rahf +bfrah+ bvrh+ 2vmhK+rahfK +bfrahK+ bvrhK-fr -brf+bvrh +bfrahKc+ 2vmhKc+ amhKc + aLKc )\rho_1^{3} + (-vmhK-rahf-bfrah-bvrh- vmhKc) \rho_1^{4}    )   \rho_{11}^2

- (+vLpK \rho_1^{-2} + (2vLpK + vLpK  + vLpKc+ vLKc- aLpKc)\rho_1^{-1} - vLpK - 2vLpK + 2aLpKc  - 2vLKc  - 2vLpKc - (fvrhK +bvrhfK+ vLpK+ vLpKc + vmhKc- aLpKc+ vLKc-frKc  -brfKc + bvrhKc )\rho_1 + (fvrh +bvrhf+fvrhK +bvrhfK+fvrhKc +bvrhfKc- 2vmhKc-rahfKc -bfrahKc- bvrhKc )\rho_1^2 - (fvrh +bvrhf+ vmhKc)\rho_1^3 )   \rho_{11}^3  - (vLpKc \rho_1^{-2} + 2vLpKc \rho_1^{-1} - vLpKc  - (fvrhKc +bvrhfKc)\rho_1 )     \rho_{11}^4    $$

assuming competition $c = 0$ and attraction $v = 0$ yields a much simpler model

$$0 = - brK \rho_1^{2}  + (br+2brK+rfK-brfK+barhK) \rho_1^{3}- (-2br-brK-frK+brfK+farhK-bfarhK-fr+brf-barh) \rho_1^{4} + (br+fr-brf-barhK-farhK+bfarhK-farh+bfarh) \rho_1^{5}+ (barh+farh-bfarh) \rho_1^{6}        + (mK + (brK-mK-2K+amhK+aLK) \rho_1 + (mK- br- 2amKh- 2aLK+2frK+brK-brahK+2K-amhK-aLK- brK) \rho_1^{2}   + (-mK+aLK-br+3amhK+2farhK+2brahK-2fr+brah-2frK+2aLK) \rho_1^{3}-  (2farh-amhK-aLK-2farhK-brahK+2fr+br)\rho_1^{4} + (2farh + brah)\rho_1^{5}  )     \rho_{11}  + (aLpK\rho_1^{-1}+ 2aLpK  + aLpK + (-frK-brfK-3aLpK+2vLK) \rho_1  + (frbrf+frK+brfK-rahfK-bfrahK+aLpK) \rho_1^{2} + (rahf +bfrah+rahfK +bfrahK-fr -brf)\rho_1^{3} + (-rahf-bfrah) \rho_1^{4}    )   \rho_{11}^2   $$
